An Analysis of Health & Lifestyle Factors Associated with Sleep Quality

### 2024-05-01 products/manuscript/Manuscript.qmd
Ref Check pt. 2000

---
title: "An Analysis of Health & Lifestyle Factors Associated with Sleep Quality"
subtitle: ""
author: Kevin Kosewick and Emma Hardin-Parker
date: "4-29-2024"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../manuscript/references_sleepdata.bib
editor: 
  markdown: 
    wrap: 72
---

@@

The dataset originally contained 373 observations for 13 variables
covering a broad spectrum of health and lifestyle variables associated
with sleep quality. The curators of the dataset did not provide
information on how or where this data was collected, so we solely relied
on the codebook for variable definitions. We have added this codebook to
the supplementary materials file for ease of access but you can also
find it on the Kaggle page for this dataset. There were no missing
values or erroneous variables in the dataset that we needed to remove.
The "Blood.Pressure" variable was transformed to reflect the individual
systolic and diastolic blood pressure measurements from each subject. We
then chose to add an additional variable, labeled 'cat_bp' to reflect
the categorical blood pressure status of a subject based on the
[American Heart Association
guidelines](https://www.heart.org/en/health-topics/high-blood-pressure).
Additionally we created a variable named 'StepsGroup' to determine the
categorical activity level of subjects in the dataset based on these
guidelines provided by [10,000 steps.org](https://www.10000steps.org.au/articles/healthy-lifestyles/counting-steps/#:~:text=The%20following%20pedometer%20indices%20have%20been%20developed%20to,day%205%20Highly%20active%20is%20more%20than%2012%2C500)
Finally, we created an additional categorical variable called
'PhysicalActivityGroup' to categorically represent the level of physical
activity reported by a subject. The levels are differentiated by 30
minute intervals of weekly physical activity. The outcome of interest is
noted as "Quality.of.Sleep" that we will reference as Sleep Quality or
Quality of Sleep throughout this report.

>>>>

---
title: "An Analysis of Health & Lifestyle Factors Associated with Sleep Quality"
subtitle: ""
author: Kevin Kosewick and Emma Hardin-Parker
date: "4-29-2024"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: dataanalysis-references.bib
csl: apa.csl 
editor: 
  markdown: 
    wrap: 72
---

@@

The dataset originally contained 373 observations for 13 variables
covering a broad spectrum of health and lifestyle variables associated
with sleep quality. The curators of the dataset did not provide
information on how or where this data was collected, so we solely relied
on the codebook for variable definitions. We have added this codebook to
the supplementary materials file for ease of access but you can also
find it on the Kaggle page for this dataset. There were no missing
values or erroneous variables in the dataset that we needed to remove.
The "Blood.Pressure" variable was transformed to reflect the individual
systolic and diastolic blood pressure measurements from each subject. We
then chose to add an additional variable, labeled 'cat_bp' to reflect
the categorical blood pressure status of a subject based on the
[American Heart Association
guidelines](https://www.heart.org/en/health-topics/high-blood-pressure).
Additionally we created a variable named 'StepsGroup' to determine the
categorical activity level of subjects in the dataset based on these
guidelines provided by [10,000 steps](https://www.10000steps.org.au/articles/healthy-lifestyles/counting-steps/#:~:text=The%20following%20pedometer%20indices%20have%20been%20developed%20to,day%205%20Highly%20active%20is%20more%20than%2012%2C500)
Finally, we created an additional categorical variable called
'PhysicalActivityGroup' to categorically represent the level of physical
activity reported by a subject. The levels are differentiated by 30
minute intervals of weekly physical activity. The outcome of interest is
noted as "Quality.of.Sleep" that we will reference as Sleep Quality or
Quality of Sleep throughout this report.
